Accessing the nucleon tensor structure in inclusive deep inelastic scattering

### 2016-07-19 1607 - JMC for g2/Paper/JMC_dis.tex
smaller corrections

The new term in Eq.{e:FLTint} only appeears in the $g_2$ structure function. Following the derivation in Ref.~\cite{ABMS}, one finds
\begin{align}
\label{e:g2}
  g_2(x_B) = g_2^{WW} + \frac{1}{2}\,\sum_a e_a^2
\biggl(
    \widetilde g_T^{a \star}(x) 
    + \int_x^1\frac{dy}{y} \widehat{g}_T^a(y) 
    + \frac{m_q}{M} (h_1^a/x)^\star(x) 
    + \frac{\mj-m_q}{M} h_1^a(x) 
\Biggr) \ ,
\end{align}
where we defined $f^*(x) = -f(x) + \int_x^1\frac{dy}{y} f(y)$. The first 4
terms coincide with the result obtained in the conventional handbag
approximation \cite{ABMS}, while the fifth is new.

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=8cm]{g2contrib}
\caption{\label{f:g2contrib} 
Different contributions to the $g_2$ structure function. 
}
\end{center}
\end{figure}

\begin{itemize}
\item large-$x$: bridges Braun's pure twist-3 theory and the data
\item samller-$x$: consttrains the small-$x$ behavior of transversity.
\end{itemize}

>>>>

The new term in Eq.\eqref{e:FLTint} only appears in the $g_2$ structure function. Following the derivation in Ref.~\cite{ABMS}, one finds
\begin{align}
\label{e:g2}
  g_2(x_B) = g_2^{WW} + \frac{1}{2}\,\sum_a e_a^2
\biggl(
    \widetilde g_T^{a \star}(x) 
    + \int_x^1\frac{dy}{y} \widehat{g}_T^a(y) 
    + \frac{m_q}{M} (h_1^a/x)^\star(x) 
    + \frac{\mj-m_q}{M} h_1^a(x) 
\Biggr) \ ,
\end{align}
where we defined $f^*(x) = -f(x) + \int_x^1\frac{dy}{y} f(y)$. The first 4
terms coincide with the result obtained in the conventional handbag
approximation \cite{ABMS}, while the fifth is new.

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=8cm]{g2contrib}
\caption{\label{f:g2contrib} 
Different contributions to the non Wandzura-Wilczek part of the $g_2$ structure function compared to the JAM15 fit of $g_2-g_2^{\text{WW}}$ \cite{JAM15}.
}
\end{center}
\end{figure}

\begin{itemize}
\item large-$x$: bridges Braun's pure twist-3 theory and the data
\item smaller-$x$: constrains the small-$x$ behavior of transversity.
\item in general, $g_2^{\text{quark}}$ is quite smaller than the other contribution, as customarily assumed.
\end{itemize}
